\section{Introduction}
%o Description of the project and the phase (implementation and testing). o If game project: Description of the game concept should be sufficiently described and explained here. o Structure of the document.

\paragraph{As today's software systems} grow bigger and more advanced, and more systems are dependent on each other, it becomes essential to learn about how systems work together, and how one can plan for this. It is also relevant, as the field of software development grows, to know how known and tested techniques and design patterns can be used to achieve new goals and develop new systems. In our project in this software architecture course, the goal was to plan out an architecture and develop a game based on this plan.

\paragraph{So we started} out with a requirements document, where we decided on what kind of game we wanted to make, and which requirements would have to be fulfilled for us to be happy about the game. The game idea was the traditional battleship, where there are two players with one board each. The board has ships on it, and each player are to try to hit the opponent's ships by guessing coordinates. We wanted to make this game on Android, with networking capabilities, meaning the two players should be able to play agains each other over the Internet. 


\paragraph{This leads us to} planning the architecture, which had some pretty extensive requirements as we wanted the game to be networked. We worked through the requirements and built the architectural requirements document. The proposed architecture went through an ATAM process with another group, and got some feedback. We then moved on to the implementation phase, which this document describes.

\paragraph{This document} consists of six parts. The first is this, the introduction. We'll then move on to describing the details of the design and implementation. We'll show the user how to play in the user manual, then describe the testing phase. We finish up this report by describing any inconsistencies we've found between our implementation and the original architectural plan, and also a review of any issues we've encountered, and what we've learned from the project.

